Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-10 ms.tex
plotting stripe vs window when the source and background apertures are more than 512 px away.:

\subsubsection{Subarray Size Comparisons}
NIRCam grism time series users can choose between full frame, SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarray sizes, which are 2048, 256, 128 and 64 pixels tall and 2048 pixels wide.
The taller subarrays have the advantage of more background pixels (or a reference star) to use in analysis.
The taller subarrays also are needed to fit the short wavelength WEAK LENS +8 PSF observed simultaneously with the long wavelength grism.
Otherwise, the WEAK LENS +4 PSF must be observed or a fraction of the WEAK LENS +8 PSF used.
The shorter subarrays have the advantage of faster frame times, permitting observations of brighter stars or more samples up the ramp than taller subarrays.
We used the same lamp LED current for the SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarrays and tuned the integration times to be similar by setting the number of RAPID groups as 8, 16 and 32 for the three subarrays respectively.
The resulting integration times are 10.8995, 10.8155 and 10.7735 seconds respectively.
No clear trend is seen in the time series shown in Figure \ref{fig:subarraySizes}.
In this example, the background aperture was always parallel to the source aperture to best remove 1/f noise.
\textbf{\textcolor{red}{Show what happens if the background aperture and source apertures are on different amplifiers and/or if they are vertical with respect to the source aperture}}

>>>>

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_larger_backsep_stripe.pdf}{0.49\textwidth}{Stripe Mode Time Series, 379 ppm}
\fig{azlab_ratio_tser_larger_backsep_window.pdf}{0.49\textwidth}{Window Mode Time series, 339 ppm}}}
\caption{When the background aperture is displaced by more than 512 pixels from the source aperture, window mode becomes slightly preferable.
}\label{fig:stripeVsWindowAZlab04LargerBacksep}
\end{figure*}

\clearpage
\subsubsection{Subarray Size Comparisons}
NIRCam grism time series users can choose between full frame, SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarray sizes, which are 2048, 256, 128 and 64 pixels tall and 2048 pixels wide.
The taller subarrays have the advantage of more background pixels (or a reference star) to use in analysis.
The taller subarrays also are needed to fit the short wavelength WEAK LENS +8 PSF observed simultaneously with the long wavelength grism.
Otherwise, the WEAK LENS +4 PSF must be observed or a fraction of the WEAK LENS +8 PSF used.
The shorter subarrays have the advantage of faster frame times, permitting observations of brighter stars or more samples up the ramp than taller subarrays.
We used the same lamp LED current for the SUBGRISM256, SUBGRISM128 and SUBGRISM64 subarrays and tuned the integration times to be similar by setting the number of RAPID groups as 8, 16 and 32 for the three subarrays respectively.
The resulting integration times are 10.8995, 10.8155 and 10.7735 seconds respectively.
No clear trend is seen in the time series shown in Figure \ref{fig:subarraySizes}.
In this example, the background aperture was always parallel to the source aperture to best remove 1/f noise.
\textbf{\textcolor{red}{Show what happens if the background aperture and source apertures are on different amplifiers and/or if they are vertical with respect to the source aperture}}
